---
format: gfm
editor: source
  markdown: 
    wrap: 72
---

# Workflow Product Retriever

MoveApps

Github repository: <https://github.com/dmpstats/Workflow-Products-Retriever>

## Description

Retrieves a Product of a given App comprised in a concurrent Workflow and combines it with the input data set, enabling data integration between multiple Workflows.

## Documentation

This App allows users to retrieve objects generated in other Workflows and combine them with the current input data. It uses MoveApps' API functionality in creating stable HTTP links for accessing up-to-date App Products, such as artifacts and output files, facilitating data exchanges between concurrent Workflows.

In practice, this App retrieves a single Product generated by a specific App within an active instance of a concurrent Workflow. The downloaded object is then appended to the input `move2::move2_loc` data according to the following operating rule:

-   If the retrieved Product is also a `move2::move2_loc` object, its data is **stacked** to the input data
-   Otherwise, the retrieved Product is **attached** to the input data via an object [attribute](https://stat.ethz.ch/R-manual/R-devel/library/base/html/attr.html) named `appended_products`.

This dual approach offers the flexibility to collect a wide range of object types and classes (`move2::move2_loc`, `move2::move2_nonloc`, `move::moveStack`, `data.frame`, `tibble`, model objects, etc.), expanding the usability of the output in downstream Apps. Currently, the App supports the retrieval of Products stored under the following file-types:

-   **`.csv`**
-   **`.txt`**
-   **`.rds`**

Users can employ multiple instances of the App whithin a Workflow, linking them sequentially or deploying them at different stages of the Workflow, to collect multiple Products from other Workflows. Furthermore, it can function as either the initial App of a Workflow or as an intermediary App.

::: callout-important
In order to use the App's functionality, the user must first create stable API links to the Workflow instance containing the desired Product(s). Instructions for generating API access credentials for your Workflows are available in the [MoveApps API Links guide](https://docs.moveapps.org/#/API).
:::

Using the Workflow instance API access credentials, users are required to specify the name of the target Product, along with either the title or the position of the App within Workflow where it is located.

#### Further details {#further-details}

As explained above, the method of appending the retrieved product to the input dataset depends on whether the fetched object is of class `move2::move2_loc` (stacked) or another class (attached via an attribute). Additionally:

-   When stacking, the App offers an option to manage duplicated track IDs between the two stacked datasets. Users can choose between merging or renaming the duplicated IDs (see `track_combine` in Section [Parameters](#parameters)).

-   In case the stacked dataset includes time-location duplicates, the App automatically removes the duplicated rows with less information. A warning message is issued.

-   If stacking involves objects with different CRS projections, the retrieved `move2::move2_loc` data is pre-projected match the CRS of the input dataset before the stacking step takes place. A warning message is issued.

-   When attaching, the retrieved product is assigned to the list element `object` of the output's `appended_products` attribute (see Section [Accessing Attached Products](#accessing-attached-products) for further details).

-   Regardless of the appending method used, metadata containing pertinent information on the retrieved product (e.g. source Workflow instance, App Title, Product filename, time of last modification) is stored in list element `metadata` of the output's `appended_products` attribute.

-   The `appended_products` attribute itself is a `list` object, meaning Products retrieved in multiple deployments of the App whithin a Workflow are added consecutively as list elements.

### Input data

A `move2::move2_loc` object.

### Output data

A `move2::move2_loc` object comprising the extra attribute `appended_products`. See sections [Further Details](#further-details) and [Accessing Attached Products](#accessing-attached-products) from more info.

### Artefacts

`appended_product_metadata.csv`: a table with the metadata of the appended Workflow Product.

### Parameters {#parameters}

**ID of Target Workflow Instance** (`usr`): the API's ID (i.e. Username) of the Workflow Instance containing the target Product (check <https://docs.moveapps.org/#/API>). Default: `NULL`.

**Password of Target Workflow Instance** (`pwd`): the API's Password of the Workflow Instance containing the target Product (check <https://docs.moveapps.org/#/API>). Default: `NULL`.

**Target Workflow Title** (`workflow_title`): the name of the Workflow with the target Product. While we recommend using the full title for clarity, aliases or acronyms are accepted. Default: `NULL`.

**Target App Title** (`app_title`): the name of the App comprising the target Product. Please ensure the name of the App is accurate. Not required if 'Target App Position in Workflow' is specified. Default: `NULL`.

**Target App Position in Workflow** (`app_pos`): Enter the position of the App containing the target Product in the Workflow's pipeline (note: initial App is in position 1). Not required if 'Target App Title' is specified. Default: `NULL`.

**Target Product Filename** (`product_file`): the target Product name. Please ensure the filename is accurate. You can omit the extension, unless multiple artifact files in the target App share the same basename. Currently supported target Product file-types: '.rds', '.csv', and '.txt'. Default: `NULL`.

**Duplicated Track IDs** (`track_combine`): If the target Product is a `move2::move2_loc` object, you can choose how to handle potential duplicated track IDs when stacking input and retrieved datasets. The 'Merge' option combines tracks with the same name, while the 'Rename' option assigns new names to non-unique tracks. Default: 'Merge'.

**Return-on-Fail** (`return_on_fail`): If input data is provided (i.e. this is not the first MoveApp in a workflow), you can choose how to handle some expected errors. Setting this to TRUE means that the input data will be passed onto the next MoveApp in the following situations:

-   No MoveApp with name **Target App Title** can be found

-   The target workflow has hit an error before reaching the target MoveApp

-   The target workflow has more than one MoveApp names **Target App Title**

    If the input data is returned due to setting `return_on_fail = TRUE`, an additional artifact will be created, `FAIL_WARNING.txt`, to alert the user that the product has *not* been successfully retrieved.

### Most common errors

If any of the inputs specified for the App parameters fails to accurately identify the target Product for retrieval, the App will generate informative error messages indicating where the misspecification occurred. Most common misspecifications include:

1.  inaccurate naming of target App title
2.  inaccurate naming of target Product filename;
3.  non-existence of the target Product in the specified App;
4.  inconsistency between the specified name of the target App and the specified position of that App in the target Workflow.

Setting **Return-on-Fail** to `TRUE` means that this MoveApp will return its input data with no retrieved data in the case of errors `1` and `3` above. It is recommended **not** to use this setting until you are confident that the target App title, filename, and position are guaranteed to be correct.

::: callout-caution
This App was developed based on the existing structure and attribute names underlying MoveApps's API framework. If there are changes to naming conventions or modifications in the way API links are constructed in the future, the code will be susceptible to HTTP request errors.
:::

### Null or error handling

Parameters `usr`, `pwd` and `product_file` must be specified, whereas at least one of `app_title` and `app_pos` needs to be provided.

The `workflow_title` parameter is optional since Workflow instance identification is already provided by `usr`. However, we strongly recommend specifying a clear and identifiable name for the target Workflow to ensure clarity when potentially referring to appended Products in downstream Apps.

### Accessing Attached Products {#accessing-attached-products}

```{r}
#| message: false
#| warning: false
#| include: false

library(move2)
library(purrr)

# Helpers
source("tests/app-testing-helpers.r")
set_interactive_testing()

# appending a move2 object
app1_output <- rFunction(
  data = readRDS("data/raw/input2.rds"),
  usr = usr, 
  pwd = pwd, 
  workflow_title = "Mock",
  app_pos = 2, 
  product_file = "data_wtime")

app_output <- rFunction(
  data = app1_output,
  usr = usr, 
  pwd = pwd, 
  workflow_title = "mock",
  app_pos = 8, 
  product_file = "app-output")

```

This section offers additional information about the App's output data. It is particularly relevant for developers wanting to use the output dataset in the development of downstream Apps. MoveApps users intending to access the output data locally can also find this section useful.

As described [above](#further-details), the `appended_products` attribute of the App's output is a `list` object storing information, and on occasion the actual data, of Products retrieved from concurrent Workflows. Each list element represents an instance of the App deployed within the current Workflow up to the current stage, containing the relevant data of the fetched Product in a sub-list with the following elements:

-   `metadata`: holds high-level information about the appended Product (e.g. original Workflow and App titles, last time modified, whether in was stacked or annexed to the input data). This element is always present in `appended_products`, regardless of the appending method applied.

-   `object`: stores the actual object(s) contained in the fetched Product when they belong to classes other than `move2:move2_loc`.

`appended_products` can be accessed using the `attr()` function. For example, the following code demonstrates how to access information and data from appended objects after deploying the App twice to retrieve Products from two different target Apps in a concurrent (mock) Workflow. First, let's verify if two Products have indeed been retrieved and appended to the App's current output object (`app_output`).

```{r}
# quick look at the app's output object
app_output
```

```{r}
# extract the data stored in output's `appended_products` attribute
apnd_prods <- attr(app_output, "appended_products")
# number of appended products
length(apnd_prods)
```

We can then query the metadata of the two appended products.

```{r}
purrr::map(apnd_prods, ~.$metadata)
```

As indicated in the `append_type` column, the first retrieved product was attached as an element of the Output's `appended_products` attribute, while the second fetched product (of class `move2:move2_loc`) was stacked to the input dataset.

To access the actual data in the first appended Product, we hoist the nested element `object` from the first element of `apnd_prods`.

```{r}
apnd_prods |> 
  purrr::pluck(1) |> 
  purrr::pluck("object")
```

Data in the second appended product was stacked to the input dataset, and hence the respective `object` element is non-existent.

```{r}
apnd_prods |> 
  purrr::pluck(2) |> 
  purrr::pluck("object")
```
